---
title: "Survey-NSF-Covid19-Nonresponse Weight Merged"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---

<style type="text/css">

body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
}
h1 { /* Header 1 */
  font-size: 18px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 16px;
  color: DarkBlue;
}
}
h3 { /* Header 3 */
    font-size: 14px;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(readxl)
library(stargazer)
library(ggplot2)
library(dplyr)
library(forcats)
library(data.table)
library(tmap)
library(readxl)
library(stargazer)
library(ggplot2)
library(dplyr)
library(forcats)
library(data.table)
library(tmap)
library(survey)
final.nsf <- read_xlsx("~/Desktop/NSF Beacon CV-19 (final-15OCT2020) weighted (CSV).xlsx",
                       col_types = c("text","numeric","text","numeric","numeric","numeric","numeric",
                                            "numeric","numeric","numeric","numeric",                                           "numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric",
                                     "numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","text","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","text","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric","numeric"))
final.nsf <- replace(final.nsf, final.nsf == 9, NA)
final.nsf$BNUName <- ifelse(final.nsf$BNUName == "Fenway", "Fenway/Kenmore", final.nsf$BNUName)
```



# Measuring behaviors


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nsf.new <- final.nsf

### April ###

nsf.new$Q7a.2 <- ifelse(nsf.new$Q7a == 1, 0, ifelse(nsf.new$Q7a == 2, 1.5, ifelse(nsf.new$Q7a == 3, 3.5, ifelse(nsf.new$Q7a == 4, 5.5,ifelse(nsf.new$Q7a == 5, 7, NA)))))

nsf.new$Q7b.2 <- ifelse(nsf.new$Q7b == 1, 0, ifelse(nsf.new$Q7b == 2, 1.5, ifelse(nsf.new$Q7b == 3, 3.5, ifelse(nsf.new$Q7b == 4, 5.5,ifelse(nsf.new$Q7b == 5, 7, NA)))))

nsf.new$Q7c.2 <- ifelse(nsf.new$Q7c == 1, 0, ifelse(nsf.new$Q7c == 2, 1.5, ifelse(nsf.new$Q7c == 3, 3.5, ifelse(nsf.new$Q7c == 4, 5.5,ifelse(nsf.new$Q7c == 5, 7, NA)))))

nsf.new$Q7d.2 <- ifelse(nsf.new$Q7d == 1, 0, ifelse(nsf.new$Q7d == 2, 1.5, ifelse(nsf.new$Q7d == 3, 3.5, ifelse(nsf.new$Q7d == 4, 5.5,ifelse(nsf.new$Q7d == 5, 7, NA)))))

nsf.new$Q7e.2 <- ifelse(nsf.new$Q7e == 1, 0, ifelse(nsf.new$Q7e == 2, 1.5, ifelse(nsf.new$Q7e == 3, 3.5, ifelse(nsf.new$Q7e == 4, 5.5,ifelse(nsf.new$Q7e == 5, 7, NA)))))

nsf.new$Q7f.2 <- ifelse(nsf.new$Q7f == 1, 0, ifelse(nsf.new$Q7f == 2, 1.5, ifelse(nsf.new$Q7f == 3, 3.5, ifelse(nsf.new$Q7f == 4, 5.5,ifelse(nsf.new$Q7f == 5, 7, NA)))))

nsf.new$Q7g.2 <- ifelse(nsf.new$Q7g == 1, 0, ifelse(nsf.new$Q7g == 2, 1.5, ifelse(nsf.new$Q7g == 3, 3.5, ifelse(nsf.new$Q7g == 4, 5.5,ifelse(nsf.new$Q7g == 5, 7, NA)))))

nsf.new$Q7h.2 <- ifelse(nsf.new$Q7h == 1, 0, ifelse(nsf.new$Q7h == 2, 1.5, ifelse(nsf.new$Q7h == 3, 3.5, ifelse(nsf.new$Q7h == 4, 5.5,ifelse(nsf.new$Q7h == 5, 7, NA)))))

nsf.new$Q7i.2 <- ifelse(nsf.new$Q7i == 1, 0, ifelse(nsf.new$Q7i == 2, 1.5, ifelse(nsf.new$Q7i == 3, 3.5, ifelse(nsf.new$Q7i == 4, 5.5,ifelse(nsf.new$Q7i == 5, 7, NA)))))

nsf.new$Q7j.2 <- ifelse(nsf.new$Q7j == 1, 0, ifelse(nsf.new$Q7j == 2, 1.5, ifelse(nsf.new$Q7j == 3, 3.5, ifelse(nsf.new$Q7j == 4, 5.5,ifelse(nsf.new$Q7j == 5, 7, NA)))))

### Summer ###

nsf.new$Q15a.2 <- ifelse(nsf.new$Q15a == 1, 0, ifelse(nsf.new$Q15a == 2, 1.5, ifelse(nsf.new$Q15a == 3, 3.5, ifelse(nsf.new$Q15a == 4, 5.5,ifelse(nsf.new$Q15a == 5, 7, NA)))))

nsf.new$Q15b.2 <- ifelse(nsf.new$Q15b == 1, 0, ifelse(nsf.new$Q15b == 2, 1.5, ifelse(nsf.new$Q15b == 3, 3.5, ifelse(nsf.new$Q15b == 4, 5.5,ifelse(nsf.new$Q15b == 5, 7, NA)))))

nsf.new$Q15c.2 <- ifelse(nsf.new$Q15c == 1, 0, ifelse(nsf.new$Q15c == 2, 1.5, ifelse(nsf.new$Q15c == 3, 3.5, ifelse(nsf.new$Q15c == 4, 5.5,ifelse(nsf.new$Q15c == 5, 7, NA)))))

nsf.new$Q15d.2 <- ifelse(nsf.new$Q15d == 1, 0, ifelse(nsf.new$Q15d == 2, 1.5, ifelse(nsf.new$Q15d == 3, 3.5, ifelse(nsf.new$Q15d == 4, 5.5,ifelse(nsf.new$Q15d == 5, 7, NA)))))

nsf.new$Q15e.2 <- ifelse(nsf.new$Q15e == 1, 0, ifelse(nsf.new$Q15e == 2, 1.5, ifelse(nsf.new$Q15e == 3, 3.5, ifelse(nsf.new$Q15e == 4, 5.5,ifelse(nsf.new$Q15e == 5, 7, NA)))))

nsf.new$Q15f.2 <- ifelse(nsf.new$Q15f == 1, 0, ifelse(nsf.new$Q15f == 2, 1.5, ifelse(nsf.new$Q15f == 3, 3.5, ifelse(nsf.new$Q15f == 4, 5.5,ifelse(nsf.new$Q15f == 5, 7, NA)))))

nsf.new$Q15g.2 <- ifelse(nsf.new$Q15g == 1, 0, ifelse(nsf.new$Q15g == 2, 1.5, ifelse(nsf.new$Q15g == 3, 3.5, ifelse(nsf.new$Q15g == 4, 5.5,ifelse(nsf.new$Q15g == 5, 7, NA)))))

nsf.new$Q15h.2 <- ifelse(nsf.new$Q15h == 1, 0, ifelse(nsf.new$Q15h == 2, 1.5, ifelse(nsf.new$Q15h == 3, 3.5, ifelse(nsf.new$Q15h == 4, 5.5,ifelse(nsf.new$Q15h == 5, 7, NA)))))

nsf.new$Q15i.2 <- ifelse(nsf.new$Q15i == 1, 0, ifelse(nsf.new$Q15i == 2, 1.5, ifelse(nsf.new$Q15i == 3, 3.5, ifelse(nsf.new$Q15i == 4, 5.5,ifelse(nsf.new$Q15i == 5, 7, NA)))))

nsf.new$Q15j.2 <- ifelse(nsf.new$Q15j == 1, 0, ifelse(nsf.new$Q15j == 2, 1.5, ifelse(nsf.new$Q15j == 3, 3.5, ifelse(nsf.new$Q15j == 4, 5.5,ifelse(nsf.new$Q15j == 5, 7, NA)))))


```

\


# High-risk behaviors in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# High-risk behaviors: mean(7b,g,i,j)
highrisk.df <- nsf.new[,c(129,134,136,137)]
nsf.new$HighRisk <- round(apply(highrisk.df, 1, mean, na.rm=TRUE),2)

mean.highrisk <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(HighRisk), funs(Wighted.mean_highrisk = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.highrisk <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(HighRisk), funs(Wighted.sd_highrisk = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

highrisk <- cbind(mean.highrisk,sd.highrisk)
highrisk <- highrisk[,-3]
```

\


## Plot for High-risk behaviors in April (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
highrisk %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_highrisk,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_highrisk,2))) +
  geom_bar(stat="identity", fill="bisque4") + ylab('High-risk behaviors in April') +
  theme_bw() + ggtitle("High-risk behaviors for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for High-risk behaviors in April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
highrisk %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_highrisk,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_highrisk,2))) +
  geom_bar(stat="identity", fill="navy") + ylab('High-risk behaviors in April') +
  theme_bw() + ggtitle("High-risk behaviors for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for High-risk behaviors in April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))
```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
highrisk.map <- merge(nbhd_geo, highrisk, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(highrisk.map) + tm_polygons(c('Wighted.mean_highrisk', 'Wighted.sd_highrisk'), palette=list("Reds","Blues"), style = "cont", title = c("Mean High risk behaviors in April", "sd High risk behaviors in April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\



## Faceted histograms by neighborhood (weighted) - High-risk behaviors in April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(nsf.new, aes(x = HighRisk, weights= MERNRWGT)) + geom_histogram(binwidth = 0.3) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('High-risk behaviors in April') +
  ggtitle("Faceted histograms by neighborhood")
 

```


\

## Faceted histograms by neighborhood (weighted) - High-risk behaviors in April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(nsf.new, aes(x = HighRisk, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + xlab('High-risk behaviors in April') +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
 

```


\

## Correlation between means and sds for High-risk behaviors in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.highrisk <- round(cor(highrisk$Wighted.mean_highrisk, highrisk$Wighted.sd_highrisk),2)
print(sprintf("The correlation between means and sds for High-risk behaviors in April is: %s", cor.highrisk))
```



\

## Anova for High-risk behaviors in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.highrisk <- aov(HighRisk ~ BNUName, data = nsf.new)
summary(anova.highrisk)
```

\

## Anova for High-risk behaviors in April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.highrisk2 <- lm(HighRisk ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.highrisk2)
```



\


# High-risk behaviors in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# High-risk behaviors: mean(15b,g,i,j)
highrisk.df2 <- nsf.new[,c(139,144,146,147)]
nsf.new$HighRisk2 <- round(apply(highrisk.df2, 1, mean, na.rm=TRUE),2)

mean.highrisk2 <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(HighRisk2), funs(Wighted.mean_highrisk = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.highrisk2 <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(HighRisk2), funs(Wighted.sd_highrisk = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

highrisk2 <- cbind(mean.highrisk2,sd.highrisk2)
highrisk2 <- highrisk2[,-3]
```

\


## Plot for High-risk behaviors in Summer (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
highrisk2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_highrisk,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_highrisk,2))) +
  geom_bar(stat="identity", fill="bisque4") + ylab('High-risk behaviors in Summer') +
  theme_bw() + ggtitle("High-risk behaviors for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for High-risk behaviors in Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
highrisk2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_highrisk,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_highrisk,2))) +
  geom_bar(stat="identity", fill="navy") + ylab('High-risk behaviors in Summer') +
  theme_bw() + ggtitle("High-risk behaviors for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for High-risk behaviors in Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))
```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
highrisk.map2 <- merge(nbhd_geo, highrisk2, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(highrisk.map2) + tm_polygons(c('Wighted.mean_highrisk', 'Wighted.sd_highrisk'), palette=list("Reds","Blues"), style = "cont", title = c("Mean High risk behaviors in Summer", "sd High risk behaviors in Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\



## Faceted histograms by neighborhood (weighted) - High-risk behaviors in Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(nsf.new, aes(x = HighRisk2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.3) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('High-risk behaviors in Summer') +
  ggtitle("Faceted histograms by neighborhood")
 

```


\

## Faceted histograms by neighborhood (weighted) - High-risk behaviors in Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(nsf.new, aes(x = HighRisk2, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + xlab('High-risk behaviors in Summer') +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
 

```


\

## Correlation between means and sds for High-risk behaviors in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.highrisk2 <- round(cor(highrisk2$Wighted.mean_highrisk, highrisk2$Wighted.sd_highrisk),2)
print(sprintf("The correlation between means and sds for High-risk behaviors in Summer is: %s", cor.highrisk2))
```



\

## Anova for High-risk behaviors in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.highrisk.sum <- aov(HighRisk2 ~ BNUName, data = nsf.new)
summary(anova.highrisk.sum)
```

\

## Anova for High-risk behaviors in Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.highrisk2.sum <- lm(HighRisk2 ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.highrisk2.sum)
```



\


# Protective in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Protective: sum(7e,f)
protective.df <- nsf.new[,c(132,133)]
nsf.new$Protective <- round(apply(protective.df, 1, sum, na.rm=TRUE),2)

mean.protective <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Protective), funs(Wighted.mean_protective = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.protective <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Protective), funs(Wighted.sd_protective = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

protective <- cbind(mean.protective,sd.protective)
protective <- protective[,-3]
```

\


## Plot for Protective in April (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
protective %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_protective,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_protective,2))) +
  geom_bar(stat="identity", fill="orange") + ylab('Protective in April') +
  theme_bw() + ggtitle("Protective for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Protective in April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
protective %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_protective,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_protective,2))) +
  geom_bar(stat="identity", fill="blue") + ylab('Protective in April') +
  theme_bw() + ggtitle("Protective for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Protective in April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
protective.map <- merge(nbhd_geo, protective, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(protective.map) + tm_polygons(c('Wighted.mean_protective', 'Wighted.sd_protective'), palette=list("Purples","Greens"), style = "cont", title = c("Mean Protective in April", "sd Protective in April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\



## Faceted histograms by neighborhood (weighted) - Protective in April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(nsf.new, aes(x = Protective, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Protective in April') +
  ggtitle("Faceted histograms by neighborhood")
 

```


\

## Faceted histograms by neighborhood (weighted) - Protective in April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(nsf.new, aes(x = Protective, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + xlab('Protective in April') +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
 

```



\

## Correlation between means and sds for Protective in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.protective <- round(cor(protective$Wighted.mean_protective, protective$Wighted.sd_protective),2)
print(sprintf("The correlation between means and sds for Protective in April is: %s", cor.protective))
```


\

## Anova for Protective in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.protective <- aov(Protective ~ BNUName, data = nsf.new)
summary(anova.protective)
```

\

## Anova for Protective in April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.protective2 <- lm(Protective ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.protective2)
```


\


# Protective in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Protective: sum(15e,f)
protective.df2 <- nsf.new[,c(142,143)]
nsf.new$Protective2 <- round(apply(protective.df2, 1, sum, na.rm=TRUE),2)

mean.protective2 <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Protective2), funs(Wighted.mean_protective = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.protective2 <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Protective2), funs(Wighted.sd_protective = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

protective2 <- cbind(mean.protective2,sd.protective2)
protective2 <- protective2[,-3]
```

\


## Plot for Protective in Summer (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
protective2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_protective,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_protective,2))) +
  geom_bar(stat="identity", fill="orange") + ylab('Protective in Summer') +
  theme_bw() + ggtitle("Protective for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Protective in Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
protective2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_protective,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_protective,2))) +
  geom_bar(stat="identity", fill="blue") + ylab('Protective in Summer') +
  theme_bw() + ggtitle("Protective for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Protective in Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
protective.map2 <- merge(nbhd_geo, protective2, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(protective.map2) + tm_polygons(c('Wighted.mean_protective', 'Wighted.sd_protective'), palette=list("Purples","Greens"), style = "cont", title = c("Mean Protective in Summer", "sd Protective in Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\



## Faceted histograms by neighborhood (weighted) - Protective in Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(nsf.new, aes(x = Protective2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Protective in Summer') +
  ggtitle("Faceted histograms by neighborhood")
 

```


\

## Faceted histograms by neighborhood (weighted) - Protective in Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(nsf.new, aes(x = Protective2, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + xlab('Protective in Summer') +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
 

```



\

## Correlation between means and sds for Protective in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.protective2 <- round(cor(protective2$Wighted.mean_protective, protective2$Wighted.sd_protective),2)
print(sprintf("The correlation between means and sds for Protective in Summer is: %s", cor.protective2))
```


\

## Anova for Protective in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.protective.sum <- aov(Protective2 ~ BNUName, data = nsf.new)
summary(anova.protective.sum)
```

\

## Anova for Protective in Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.protective2.sum <- lm(Protective2 ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.protective2.sum)
```
\



# Food in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Food: sum(7c,d)
food.df <- nsf.new[,c(130,131)]
nsf.new$Food <- round(apply(food.df, 1, sum, na.rm=TRUE),2)

mean.food <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Food), funs(Wighted.mean_food = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.food <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Food), funs(Wighted.sd_food = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

food <- cbind(mean.food,sd.food)
food <- food[,-3]
```

\


## Plot for Food in April (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
food %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_food,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_food,2))) +
  geom_bar(stat="identity", fill="darkcyan") + ylab('Food in April') +
  theme_bw() + ggtitle("Food for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Foodin April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
food %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_food,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_food,2))) +
  geom_bar(stat="identity", fill="darkolivegreen4") + ylab('Food in April') +
  theme_bw() + ggtitle("Food for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Food in April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))


```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
food.map <- merge(nbhd_geo, food, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(food.map) + tm_polygons(c('Wighted.mean_food', 'Wighted.sd_food'), palette=list("Reds","Greens"), style = "cont", title = c("Mean Food in April", "sd Food in April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\


## Faceted histograms by neighborhood (weighted) - Food in April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(nsf.new, aes(x = Food, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Food in April') +
  ggtitle("Faceted histograms by neighborhood")
 

```


\

## Faceted histograms by neighborhood (weighted) - Food in April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(nsf.new, aes(x = Food, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + xlab('Food in April') +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
```



\

## Correlation between means and sds for Food in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.food <- round(cor(food$Wighted.mean_food, food$Wighted.sd_food),2)
print(sprintf("The correlation between means and sds for Food in April is: %s", cor.food))
```


\

## Anova for Food in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.food <- aov(Food ~ BNUName, data = nsf.new)
summary(anova.food)
```

\

## Anova for Food in April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.food2 <- lm(Food ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.food2)
```






# Food in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Food: sum(15c,d)
food.df2 <- nsf.new[,c(140,141)]
nsf.new$Food2 <- round(apply(food.df2, 1, sum, na.rm=TRUE),2)

mean.food2 <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Food2), funs(Wighted.mean_food = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.food2 <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Food2), funs(Wighted.sd_food = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

food2 <- cbind(mean.food2,sd.food2)
food2 <- food2[,-3]
```

\


## Plot for Food in Summer (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
food2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_food,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_food,2))) +
  geom_bar(stat="identity", fill="darkcyan") + ylab('Food in Summer') +
  theme_bw() + ggtitle("Food for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Food in Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
food2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_food,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_food,2))) +
  geom_bar(stat="identity", fill="darkolivegreen4") + ylab('Food in Summer') +
  theme_bw() + ggtitle("Food for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Food in Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))


```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
food.map2 <- merge(nbhd_geo, food2, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(food.map2) + tm_polygons(c('Wighted.mean_food', 'Wighted.sd_food'), palette=list("Reds","Greens"), style = "cont", title = c("Mean Food in Summer", "sd Food in Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\


## Faceted histograms by neighborhood (weighted) - Food in Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(nsf.new, aes(x = Food2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Food in Summer') +
  ggtitle("Faceted histograms by neighborhood")
 

```


\

## Faceted histograms by neighborhood (weighted) - Food in Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(nsf.new, aes(x = Food2, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + xlab('Food in Summer') +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
```



\

## Correlation between means and sds for Food in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.food2 <- round(cor(food2$Wighted.mean_food, food2$Wighted.sd_food),2)
print(sprintf("The correlation between means and sds for Food in Summer is: %s", cor.food2))
```


\

## Anova for Food in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.food.sum <- aov(Food2 ~ BNUName, data = nsf.new)
summary(anova.food.sum)
```

\

## Anova for Food in Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.food2.sum <- lm(Food2 ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.food2.sum)
```



\



# Transit
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Transit: 7/15a (stand-alone that we want to analyze)
mean.transit <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Q7a.2, Q15a.2), funs(Wighted.mean_transit = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.transit <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Q7a.2, Q15a.2), funs(Wighted.sd_transit = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

transit <- cbind(mean.transit,sd.transit)
transit <- transit[,-4]
names(transit)[2] <- 'Transit.April.mean' 
names(transit)[3] <- 'Transit.Summer.mean'
names(transit)[4] <- 'Transit.April.sd' 
names(transit)[5] <- 'Transit.Summer.sd'
```


\


## Plot for Transit (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
transit.1 <- melt(transit[,c(1,2,3)]) 
transit.1 %>%
  ggplot(aes(x=BNUName, y=value, fill=variable)) +
  geom_bar(stat="identity", position=position_dodge()) + ylab('Transit') +
  theme_bw() + ggtitle("Transit for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) +
  scale_fill_brewer(palette="Reds") + labs(fill='Transit')
```


## Plot for Transit (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
transit.2 <- melt(transit[,c(1,4,5)]) 
transit.2 %>%
  ggplot(aes(x=BNUName, y=value, fill=variable)) +
  geom_bar(stat="identity", position=position_dodge()) + ylab('Transit') +
  theme_bw() + ggtitle("Transit for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8))  + labs(fill='Transit')
```


\


## Maps for Transit 
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
transit.map <- merge(nbhd_geo, transit, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(transit.map) + tm_polygons(c('Transit.April.mean','Transit.Summer.mean','Transit.April.sd','Transit.Summer.sd'), palette=list("Reds","Greens","Blues","Purples"), style = "cont") + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\



## Faceted histograms by neighborhood (weighted) - Transit in April and Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)
ggplot(nsf.new, aes(x = Q7a.2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + scale_x_continuous("Transit in April", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood")

ggplot(nsf.new, aes(x = Q15a.2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + scale_x_continuous("Transit in Summer", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood")
```


\

## Faceted histograms by neighborhood (weighted) - Transit in April and Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(nsf.new, aes(x = Q7a.2, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + scale_x_continuous("Transit in April", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

ggplot(nsf.new, aes(x = Q15a.2), weights= MERNRWGT) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + scale_x_continuous("Transit in Summer", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
```

\

## Correlation between means and sds for Transit in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.transit.april <- round(cor(transit$Transit.April.mean, transit$Transit.April.sd),2)
print(sprintf("The correlation between means and sds for Transit in April is: %s", cor.transit.april))
```

\

## Correlation between means and sds for Transit in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.transit.summer <- round(cor(transit$Transit.Summer.mean, transit$Transit.Summer.sd),2)
print(sprintf("The correlation between means and sds for Transit in Summer is: %s", cor.transit.summer))
```

\

## Anova for Transit in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.transit.april <- aov(Q7a.2 ~ BNUName, data = nsf.new)
summary(anova.transit.april)
```

\

## Anova for Transit in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.transit.summer <- aov(Q15a.2 ~ BNUName, data = nsf.new)
summary(anova.transit.summer)
```




\

## Anova for Transit in April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.transit.april.2 <- lm(Q7a.2 ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.transit.april.2)
```


\


## Anova for Transit in Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.transit.summer.2 <- lm(Q15a.2 ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.transit.summer.2)
```



\



# Exercise
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Exercise: 7/15h (stand-alone)
# exercise.df <- nsf.new[,c(137,147)]

mean.exercise <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Q7h.2, Q15h.2), funs(Wighted.mean_exercise = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.exercise <- nsf.new %>%
  group_by(BNUName) %>% 
  summarise_at(vars(Q7h.2, Q15h.2), funs(Wighted.sd_exercise = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

exercise <- cbind(mean.exercise,sd.exercise)
exercise <- exercise[,-4]
names(exercise)[2] <- 'Exercise.April.mean' 
names(exercise)[3] <- 'Exercise.Summer.mean'
names(exercise)[4] <- 'Exercise.April.sd' 
names(exercise)[5] <- 'Exercise.Summer.sd'
```


\


## Plot for Exercise (Wighted mean)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
exercise.1 <- melt(exercise[,c(1,2,3)]) 
exercise.1 %>%
  ggplot(aes(x=BNUName, y=value, fill=variable)) +
  geom_bar(stat="identity", position=position_dodge()) + ylab('Exercise') +
  theme_bw() + ggtitle("Exercise for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) +
  scale_fill_brewer(palette="Blues") + labs(fill='Exercise')
```


## Plot for Exercise (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
exercise.2 <- melt(exercise[,c(1,4,5)]) 
exercise.2 %>%
  ggplot(aes(x=BNUName, y=value, fill=variable)) +
  geom_bar(stat="identity", position=position_dodge()) + ylab('Exercise') +
  theme_bw() + ggtitle("Exercise for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8))  + labs(fill='Exercise') +
  scale_fill_brewer(palette="Greens")
```


\


## Maps for Exercise 
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
exercise.map <- merge(nbhd_geo, exercise, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(exercise.map) + tm_polygons(c('Exercise.April.mean','Exercise.Summer.mean','Exercise.April.sd','Exercise.Summer.sd'), palette=list("Reds","Greens","Blues","Purples"), style = "cont") + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\


\

## Faceted histograms by neighborhood (weighted) - Exercise in April and Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)
ggplot(nsf.new, aes(x = Q7h.2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + scale_x_continuous("Exercise in April", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood")

ggplot(nsf.new, aes(x = Q15h.2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.8) + theme_bw() +
  facet_wrap(~ BNUName) + scale_x_continuous("Exercise in Summer", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood")
```


\

## Faceted histograms by neighborhood (weighted) - Exercise in April and Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(nsf.new, aes(x = Q7h.2, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + scale_x_continuous("Exercise in April", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

ggplot(nsf.new, aes(x = Q15h.2), weights= MERNRWGT) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() + ylab("Proportion") +
  facet_wrap(~ BNUName) + scale_x_continuous("Exercise in Summer", breaks = c(0,1.5, 3.5, 5.5,7)) +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
```


\

## Correlation between means and sds for Exercise in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.exercise.april <- round(cor(exercise$Exercise.April.mean, exercise$Exercise.April.sd),2)
print(sprintf("The correlation between means and sds for Exercise in April is: %s", cor.exercise.april))
```

\

## Correlation between means and sds for Exercise in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.exercise.summer <- round(cor(exercise$Exercise.Summer.mean, exercise$Exercise.Summer.sd),2)
print(sprintf("The correlation between means and sds for Exercise in Summer is: %s", cor.exercise.summer))
```

\

## Anova for Exercise in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.exercise.april <- aov(Q7h.2 ~ BNUName, data = nsf.new)
summary(anova.exercise.april)
```

\

## Anova for Exercise in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.exercise.summer <- aov(Q15h.2 ~ BNUName, data = nsf.new)
summary(anova.exercise.summer)
```




\

## Anova for Exercise in April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.exercise.april.2 <- lm(Q7h.2 ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.exercise.april.2)
```


\


## Anova for Exercise in Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.exercise.summer.2 <- lm(Q15h.2 ~ BNUName, data = nsf.new, weights = MERNRWGT)
anova(anova.exercise.summer.2)
```


\



# Factor1: High Risk Exposures, April
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_APR1
mean.RBEH_APR1 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR1), funs(Wighted.mean_APR1 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_APR1 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR1), funs(Wighted.sd_APR1 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_APR1 <- cbind(mean.RBEH_APR1,sd.RBEH_APR1)
RBEH_APR1 <- RBEH_APR1[,-3]
```



## Plot for Factor1: High Risk Exposures, April (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR1 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_APR1,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_APR1,2))) +
  geom_bar(stat="identity", fill="bisque4") + ylab('Factor1: High Risk Exposures, April (mean)') +
  theme_bw() + ggtitle("Factor1: High Risk Exposures, April for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Factor1: High Risk Exposures, April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR1 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_APR1,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_APR1,2))) +
  geom_bar(stat="identity", fill="navy") + ylab('Factor1: High Risk Exposures, April (sd)') +
  theme_bw() + ggtitle("Factor1: High Risk Exposures, April for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Factor1: High Risk Exposures, April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR1.map <- merge(nbhd_geo, RBEH_APR1, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(RBEH_APR1.map) + tm_polygons(c('Wighted.mean_APR1', 'Wighted.sd_APR1'), palette=list("Reds","Blues"), style = "cont", title = c("Mean High Risk April", "sd High Risk April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```

\



## Faceted histograms by neighborhood (weighted) - Factor1: High Risk Exposures, April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_APR1, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor1: High Risk Exposures, April') +
  ggtitle("Faceted histograms by neighborhood")
```



\


## Faceted histograms by neighborhood (weighted) - Factor1: High Risk Exposures, April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(final.nsf, aes(x = RBEH_APR1, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor1: High Risk Exposures, April') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```




\

## Correlation between means and sds for Factor1: High Risk Exposures, April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_APR1 <- round(cor(RBEH_APR1$Wighted.mean_APR1, RBEH_APR1$Wighted.sd_APR1),2)
print(sprintf("The correlation between means and sds for Factor1: High Risk Exposures, April is: %s", cor.RBEH_APR1))
```


\

## Anova for Factor1: High Risk Exposures, April without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR1 <- aov(RBEH_APR1 ~ BNUName, data = final.nsf)
summary(anova.RBEH_APR1)
```

\

## Anova for Factor1: High Risk Exposures, April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR1.2 <- lm(RBEH_APR1 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_APR1.2)
```


\


# Factor2: Food & Trolley, April
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_APR2
mean.RBEH_APR2 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR2), funs(Wighted.mean_APR2 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_APR2 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR2), funs(Wighted.sd_APR2 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_APR2 <- cbind(mean.RBEH_APR2,sd.RBEH_APR2)
RBEH_APR2 <- RBEH_APR2[,-3]
```



## Plot for Factor2: Food & Trolley, April (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_APR2,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_APR2,2))) +
  geom_bar(stat="identity", fill="darkgoldenrod4") + ylab('Factor2: Food & Trolley, April (mean)') +
  theme_bw() + ggtitle("Factor2: Food & Trolley, April for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Factor2: Food & Trolley, April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_APR2,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_APR2,2))) +
  geom_bar(stat="identity", fill="cornsilk4") + ylab('Factor2: Food & Trolley, April (sd)') +
  theme_bw() + ggtitle("Factor2: Food & Trolley, April for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Factor2: Food & Trolley, April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR2.map <- merge(nbhd_geo, RBEH_APR2, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(RBEH_APR2.map) + tm_polygons(c('Wighted.mean_APR2', 'Wighted.sd_APR2'), palette=list("Oranges","Greens"), style = "cont", title = c("Mean Food & Trolley April", "sd Food & Trolley April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\



## Faceted histograms by neighborhood (weighted) - Factor2: Food & Trolley, April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(final.nsf, aes(x = RBEH_APR2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor2: Food & Trolley, April') + 
  ggtitle("Faceted histograms by neighborhood")
```



\


## Faceted histograms by neighborhood (weighted) - Factor2: Food & Trolley, April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_APR2, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..))) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor2: Food & Trolley, April') + ylab("Proportion") +
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")
```



\

## Correlation between means and sds for Factor2: Food & Trolley, April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_APR2 <- round(cor(RBEH_APR2$Wighted.mean_APR2, RBEH_APR2$Wighted.sd_APR2),2)
print(sprintf("The correlation between means and sds for Factor2: Food & Trolley, April is: %s", cor.RBEH_APR2))
```


\

## Anova for Factor2: Food & Trolley, April without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR2 <- aov(RBEH_APR2 ~ BNUName, data = final.nsf)
summary(anova.RBEH_APR2)
```

\

## Anova for Factor2: Food & Trolley, April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR2.2 <- lm(RBEH_APR2 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_APR2.2)
```




\

# Factor3: Ordered Food & Groceries, April
\



```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_APR4
mean.RBEH_APR3 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR4), funs(Wighted.mean_APR3 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_APR3 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR4), funs(Wighted.sd_APR3 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_APR3 <- cbind(mean.RBEH_APR3,sd.RBEH_APR3)
RBEH_APR3 <- RBEH_APR3[,-3]
```

\

## Plot for Factor3: Ordered Food & Groceries, April (Wighted mean)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR3 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_APR3,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_APR3,2))) +
  geom_bar(stat="identity", fill="darkslategray") + ylab('Factor3: Ordered Food & Groceries, April (mean)') +
  theme_bw() + ggtitle("Factor3: Ordered Food & Groceries, April for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```
\


## Plot for Factor3: Ordered Food & Groceries, April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR3 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_APR3,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_APR3,2))) +
  geom_bar(stat="identity", fill="ivory4") + ylab('Factor3: Ordered Food & Groceries, April (sd)') +
  theme_bw() + ggtitle("Factor3: Ordered Food & Groceries, April for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps Factor3: Ordered Food & Groceries, April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR3.map <- merge(nbhd_geo, RBEH_APR3, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)
tmap_mode('view')
tm_shape(RBEH_APR3.map) + tm_polygons(c('Wighted.mean_APR3', 'Wighted.sd_APR3'), palette=list("Oranges","Greens"), style = "cont", title = c("Mean Food & Groceries April", "sd Food & Groceries April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\


## Faceted histograms by neighborhood (weighted) - Factor3: Ordered Food & Groceries, April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_APR4, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor3: Ordered Food & Groceries, April') +
  ggtitle("Faceted histograms by neighborhood")
```



\



## Faceted histograms by neighborhood (weighted) - Factor3: Ordered Food & Groceries, April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(ggplot2)

ggplot(final.nsf, aes(x = RBEH_APR4, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor3: Ordered Food & Groceries, April') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```



\

## Correlation between means and sds for Factor3: Ordered Food & Groceries, April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_APR3 <- round(cor(RBEH_APR3$Wighted.mean_APR3, RBEH_APR3$Wighted.sd_APR3),2)
print(sprintf("The correlation between means and sds for Factor3: Ordered Food & Groceries, April is: %s", cor.RBEH_APR3))
```


\

## Anova for Factor3: Ordered Food & Groceries, April without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR3 <- aov(RBEH_APR4 ~ BNUName, data = final.nsf)
summary(anova.RBEH_APR3)
```

\

## Anova for Factor3: Ordered Food & Groceries, April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR3 <- lm(RBEH_APR4 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_APR3)
```

\




# Factor4: Exercise & Got Groceries, April
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_APR4
mean.RBEH_APR4 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR3), funs(Wighted.mean_APR4 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_APR4 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_APR3), funs(Wighted.sd_APR4 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_APR4 <- cbind(mean.RBEH_APR4,sd.RBEH_APR4)
RBEH_APR4 <- RBEH_APR4[,-3]
```



## Plot for Factor4: Exercise & Got Groceries, April (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR4 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_APR4,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_APR4,2))) +
  geom_bar(stat="identity", fill="deeppink4") + ylab('Factor4: Exercise & Got Groceries, April (mean)') +
  theme_bw() + ggtitle("Factor4: Exercise & Got Groceries, April for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Factor4: Exercise & Got Groceries, April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR4 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_APR4,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_APR4,2))) +
  geom_bar(stat="identity", fill="lavenderblush4") + ylab('Factor4: Exercise & Got Groceries, April (sd)') + theme_bw() + ggtitle("Factor4: Exercise & Got Groceries, April for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Factor4: Exercise & Got Groceries, April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\



```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_APR4.map <- merge(nbhd_geo, RBEH_APR4, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)
tmap_mode('view')
tm_shape(RBEH_APR4.map) + tm_polygons(c('Wighted.mean_APR4', 'Wighted.sd_APR4'), palette=list("Reds","Greens"), style = "cont", title = c("Mean Exercise & Got Groceries April", "sd Exercise & Got Groceries April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```



\

## Faceted histograms by neighborhood (weighted) - Factor4: Exercise & Got Groceries, April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_APR3, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor4: Exercise & Got Groceries, April') +
  ggtitle("Faceted histograms by neighborhood")
```




\


## Faceted histograms by neighborhood (weighted) - Factor4: Exercise & Got Groceries, April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = RBEH_APR3, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor4: Exercise & Got Groceries, April') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```



\


## Correlation between means and sds for Factor4: Exercise & Got Groceries, April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_APR4 <- round(cor(RBEH_APR4$Wighted.mean_APR4, RBEH_APR4$Wighted.sd_APR4),2)
print(sprintf("The correlation between means and sds for Factor4: Exercise & Got Groceries, April is: %s", cor.RBEH_APR4))
```


\

## Anova for Factor4: Exercise & Got Groceries, April without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR4 <- aov(RBEH_APR3 ~ BNUName, data = final.nsf)
summary(anova.RBEH_APR4)
```

\

## Anova for Factor4: Exercise & Got Groceries, April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_APR4 <- lm(RBEH_APR3 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_APR4)
```


\


# Factor1: High Risk Exposures, Summer
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_SMR1
mean.RBEH_SMR1 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR1), funs(Wighted.mean_SMR1 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_SMR1 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR1), funs(Wighted.sd_SMR1 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_SMR1 <- cbind(mean.RBEH_SMR1,sd.RBEH_SMR1)
RBEH_SMR1 <- RBEH_SMR1[,-3]
```
\


## Plot for Factor1: High Risk Exposures, Summer (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR1 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_SMR1,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_SMR1,2))) +
  geom_bar(stat="identity", fill="bisque4") + ylab('Factor1: High Risk Exposures, Summer (mean)') +
  theme_bw() + ggtitle("Factor1: High Risk Exposures, Summer for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```
\


## Plot for Factor1: High Risk Exposures, Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR1 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_SMR1,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_SMR1,2))) +
  geom_bar(stat="identity", fill="navy") + ylab('Factor1: High Risk Exposures, Summer (sd)') +
  theme_bw() + ggtitle("Factor1: High Risk Exposures, Summer for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Factor1: High Risk Exposures Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```


\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR1.map <- merge(nbhd_geo, RBEH_SMR1, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)
tmap_mode('view')
tm_shape(RBEH_SMR1.map) + tm_polygons(c('Wighted.mean_SMR1', 'Wighted.sd_SMR1'), palette=list("Reds","Blues"), style = "cont", title = c("Mean High Risk Summer", "sd High Risk Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\

## Faceted histograms by neighborhood (weighted) - Factor1: High Risk Exposures Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_SMR1, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor1: High Risk Exposures Summer') +
  ggtitle("Faceted histograms by neighborhood")
```



\

## Faceted histograms by neighborhood (weighted) - Factor1: High Risk Exposures Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = RBEH_SMR1, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor1: High Risk Exposures Summer') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```

\


## Correlation between means and sds for Factor1: High Risk Exposures Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_SMR1 <- round(cor(RBEH_SMR1$Wighted.mean_SMR1, RBEH_SMR1$Wighted.sd_SMR1),2)
print(sprintf("The correlation between means and sds for Factor1: High Risk Exposures Summer is: %s", cor.RBEH_SMR1))
```


\

## Anova for Factor1: High Risk Exposures Summer without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR1 <- aov(RBEH_SMR1 ~ BNUName, data = final.nsf)
summary(anova.RBEH_SMR1)
```

\

## Anova for Factor1: High Risk Exposures Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR1 <- lm(RBEH_SMR1 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_SMR1)
```



\


# Factor2: Food & Trolley, Summer
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_SMR2
mean.RBEH_SMR2 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR2), funs(Wighted.mean_SMR2 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_SMR2 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR2), funs(Wighted.sd_SMR2 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_SMR2 <- cbind(mean.RBEH_SMR2,sd.RBEH_SMR2)
RBEH_SMR2 <- RBEH_SMR2[,-3]
```

\


## Plot for Factor2: Food & Trolley, Summer (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_SMR2,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_SMR2,2))) +
  geom_bar(stat="identity", fill="darkgoldenrod4") + ylab('Factor2: Food & Trolley, Summer (mean)') +
  theme_bw() + ggtitle("Factor2: Food & Trolley, Summer for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Factor2: Food & Trolley, Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR2 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_SMR2,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_SMR2,2))) +
  geom_bar(stat="identity", fill="cornsilk4") + ylab('Factor2: Food & Trolley, Summer (sd)') +
  theme_bw() + ggtitle("Factor2: Food & Trolley, Summer for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Factor2: Food & Trolley, Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR2.map <- merge(nbhd_geo, RBEH_SMR2, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(RBEH_SMR2.map) + tm_polygons(c('Wighted.mean_SMR2', 'Wighted.sd_SMR2'), palette=list("Oranges","Greens"), style = "cont", title = c("Mean Food & Trolley Summer", "sd Food & Trolley Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\

## Faceted histograms by neighborhood (weighted) - Factor2: Food & Trolley, Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_SMR2, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor2: Food & Trolley, Summer') +
  ggtitle("Faceted histograms by neighborhood")
```


\

## Faceted histograms by neighborhood (weighted) - Factor2: Food & Trolley, Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = RBEH_SMR2, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor2: Food & Trolley, Summer') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```


\


## Correlation between means and sds for Factor2: Food & Trolley, Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_SMR2 <- round(cor(RBEH_SMR2$Wighted.mean_SMR2, RBEH_SMR2$Wighted.sd_SMR2),2)
print(sprintf("The correlation between means and sds for Factor2: Food & Trolley, Summer is: %s", cor.RBEH_SMR2))
```


\

## Anova for Factor2: Food & Trolley, Summer without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR2 <- aov(RBEH_SMR2 ~ BNUName, data = final.nsf)
summary(anova.RBEH_SMR2)
```

\

## Anova for Factor2: Food & Trolley, Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR2 <- lm(RBEH_SMR2 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_SMR2)
```

\



# Factor3: Ordered Food & Groceries, Summer
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_SMR3
mean.RBEH_SMR3 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR3), funs(Wighted.mean_SMR3 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_SMR3 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR3), funs(Wighted.sd_SMR3 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_SMR3 <- cbind(mean.RBEH_SMR3,sd.RBEH_SMR3)
RBEH_SMR3 <- RBEH_SMR3[,-3]
```

\

## Plot for Factor3: Ordered Food & Groceries, Summer (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR3 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_SMR3,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_SMR3,2))) +
  geom_bar(stat="identity", fill="darkslategray") + ylab('Factor3: Ordered Food & Groceries, Summer (mean)') +
  theme_bw() + ggtitle("Factor3: Ordered Food & Groceries, Summer for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```
\


## Plot for Factor3: Ordered Food & Groceries, Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR3 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_SMR3,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_SMR3,2))) +
  geom_bar(stat="identity", fill="ivory4") + ylab('Factor3: Ordered Food & Groceries, Summer (sd)') +
  theme_bw() + ggtitle("Factor3: Ordered Food & Groceries, Summer for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8))  
```


\


## Maps Factor3: Ordered Food & Groceries, Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR3.map <- merge(nbhd_geo, RBEH_SMR3, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(RBEH_SMR3.map) + tm_polygons(c('Wighted.mean_SMR3', 'Wighted.sd_SMR3'), palette=list("Oranges","Greens"), style = "cont", title = c("Mean Ordered Food & Groceries Summer", "sd Ordered Food & Groceries Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\

## Faceted histograms by neighborhood (weighted) - Factor3: Ordered Food & Groceries, Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_SMR3, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor3: Ordered Food & Groceries, Summer') +
  ggtitle("Faceted histograms by neighborhood")
```



\

## Faceted histograms by neighborhood (weighted) - Factor3: Ordered Food & Groceries, Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = RBEH_SMR3, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor3: Ordered Food & Groceries, Summer') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```




\

## Correlation between means and sds for Factor3: Ordered Food & Groceries, Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_SMR3 <- round(cor(RBEH_SMR3$Wighted.mean_SMR3, RBEH_SMR3$Wighted.sd_SMR3),2)
print(sprintf("The correlation between means and sds for Factor3: Ordered Food & Groceries, Summer is: %s", cor.RBEH_SMR3))
```


\

## Anova for Factor3: Ordered Food & Groceries, Summer without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR3 <- aov(RBEH_SMR3 ~ BNUName, data = final.nsf)
summary(anova.RBEH_SMR3)
```

\

## Anova for Factor3: Ordered Food & Groceries, Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR3 <- lm(RBEH_SMR3 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_SMR3)
```

\



# Factor4: Exercise & Got Groceries, Summer
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# RBEH_SMR4
mean.RBEH_SMR4 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR4), funs(Wighted.mean_SMR4 = weighted.mean(., MERNRWGT, na.rm=TRUE)))


sd.RBEH_SMR4 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(RBEH_SMR4), funs(Wighted.sd_SMR4 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

RBEH_SMR4 <- cbind(mean.RBEH_SMR4,sd.RBEH_SMR4)
RBEH_SMR4 <- RBEH_SMR4[,-3]
```



## Plot for Factor4: Exercise & Got Groceries, Summer (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR4 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean_SMR4,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean_SMR4,2))) +
  geom_bar(stat="identity", fill="deeppink4") + ylab('Factor4: Exercise & Got Groceries, Summer (mean)') +
  theme_bw() + ggtitle("Factor4: Factor4: Exercise & Got Groceries, Summer for each neighborhood (mean)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Factor4: Exercise & Got Groceries, Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
RBEH_SMR4 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd_SMR4,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd_SMR4,2))) +
  geom_bar(stat="identity", fill="lavenderblush4") + ylab('Factor4: Exercise & Got Groceries, Summer (sd)') + theme_bw() + ggtitle("Factor4: Exercise & Got Groceries, Summer for each neighborhood (sd)") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Factor4: Exercise & Got Groceries, Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\



```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

RBEH_SMR4.map <- merge(nbhd_geo, RBEH_SMR4, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(RBEH_SMR4.map) + tm_polygons(c('Wighted.mean_SMR4', 'Wighted.sd_SMR4'), palette=list("Reds","Greens"), style = "cont", title = c("Mean Exercise & Got Groceries Summer", "sdExercise & Got Groceries Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```



\

## Faceted histograms by neighborhood (weighted) - Factor4: Exercise & Got Groceries, Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = RBEH_SMR4, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor4: Exercise & Got Groceries, Summer') +
  ggtitle("Faceted histograms by neighborhood")
```



\

## Faceted histograms by neighborhood (weighted) - Factor4: Exercise & Got Groceries, Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = RBEH_SMR4, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Factor4: Exercise & Got Groceries, Summer') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```



\

## Correlation between means and sds for Factor4: Exercise & Got Groceries, Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.RBEH_SMR4 <- round(cor(RBEH_SMR4$Wighted.mean_SMR4, RBEH_SMR4$Wighted.sd_SMR4),2)
print(sprintf("The correlation between means and sds for Factor4: Exercise & Got Groceries, Summer is: %s", cor.RBEH_SMR4))
```


\

## Anova for Factor4: Exercise & Got Groceries, Summer without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR4 <- aov(RBEH_SMR4 ~ BNUName, data = final.nsf)
summary(anova.RBEH_SMR4)
```

\

## Anova for Factor4: Exercise & Got Groceries, Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.RBEH_SMR4 <- lm(RBEH_SMR4 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.RBEH_SMR4)
```


\


# Perceived Risk (risk3) ==> 4=large risk
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Mean Risk Perception: (Q35-Q37, 4=large risk)
mean.risk3 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(risk3), funs(Wighted.mean.Risk3 = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.risk3 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(risk3), funs(Wighted.sd.Risk3 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

risk3 <- cbind(mean.risk3,sd.risk3 )
risk3 <- risk3[,-3]
```

\

## Plot for Perceived Risk (risk3) (Wighted mean)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
risk3 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean.Risk3,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean.Risk3,2))) +
  geom_bar(stat="identity", fill="bisque4") + ylab('Perceived risk (Wighted mean)') +
  theme_bw() + ggtitle("Perceived risk (Wighted mean) for each neighborhood") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```
\

## Plot for Perceived Risk (risk3) (Wighted sd)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
risk3 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd.Risk3,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd.Risk3,2))) +
  geom_bar(stat="identity", fill="navy") + ylab('Perceived risk (Wighted sd)') +
  theme_bw() + ggtitle("Perceived risk (Wighted sd) for each neighborhood") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Perceived Risk (risk3)

\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

risk3.map <- merge(nbhd_geo, risk3, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(risk3.map) + tm_polygons(c('Wighted.mean.Risk3','Wighted.sd.Risk3'), palette=list("Reds","Blues"), style = "cont", title = c("Mean Perceived Risk", "sd Perceived Risk")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\

## Faceted histograms by neighborhood (weighted) - Perceived Risk - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = risk3, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Perceived Risk') +
  ggtitle("Faceted histograms by neighborhood")
```



\

## Faceted histograms by neighborhood (weighted) - Perceived Risk - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = risk3, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Perceived Risk') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```


\

## Correlation between means and sds for Perceived Risk
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.risk3 <- round(cor(risk3$Wighted.mean.Risk3, risk3$Wighted.sd.Risk3),2)
print(sprintf("The correlation between means and sds for Perceived Risk is: %s", cor.risk3))
```


\

## Anova for Perceived Risk without weights
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.risk3 <- aov(risk3 ~ BNUName, data = final.nsf)
summary(anova.risk3)
```



\

## Anova for Perceived Risk with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.2 <- lm(risk3 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.2)
```


\


# Guideline Importance (guideimp4) ==> 4=extremely
\

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Mean Importance of Guidelines Adherence: (Q30-Q33), 4=extremely
mean.guide <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(guideimp4), funs(Wighted.mean.Guideimp = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.guide <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(guideimp4), funs(Wighted.sd.Guideimp = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

guide <- cbind(mean.guide,sd.guide)
guide <- guide[,-3]
```

\

## Plot for Guideline Importance (Wighted mean)


\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
guide %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean.Guideimp ,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean.Guideimp,2))) +
  geom_bar(stat="identity", fill="darkorange4") + ylab('Guideline Importance (Wighted mean)') +
  theme_bw() + ggtitle("Guideline Importance (Wighted mean) for each neighborhood") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```
\

## Plot for Guideline Importance (Wighted sd)

\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
guide %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd.Guideimp,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd.Guideimp,2))) +
  geom_bar(stat="identity", fill="darksalmon") + ylab('Guideline Importance (Wighted sd)') +
  theme_bw() + ggtitle("Guideline Importance (Wighted sd) for each neighborhood") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Guideline Importance

\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))

```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

guide.map <- merge(nbhd_geo, guide, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(guide.map) + tm_polygons(c('Wighted.mean.Guideimp','Wighted.sd.Guideimp'), palette=list("Oranges","Purples"), style = "cont", title = c("Mean Guideline Importance", "sd Guideline Importance")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```




\

## Faceted histograms by neighborhood (weighted) - Guideline Importance - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = guideimp4, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Guideline Importance') +
  ggtitle("Faceted histograms by neighborhood")
```


\

## Faceted histograms by neighborhood (weighted) - Guideline Importance - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = guideimp4, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Guideline Importance') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```



\


## Correlation between means and sds for Guideline Importance
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.guide <- round(cor(guide$Wighted.mean.Guideimp, guide$Wighted.sd.Guideimp),2)
print(sprintf("The correlation between means and sds for Guideline Importance is: %s", cor.guide))
```


\

## Anova for Guideline Importance without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.guide <- aov(guideimp4 ~BNUName, data = final.nsf)
summary(anova.guide)
```

\

## Anova for Guideline Importance with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.2 <- lm(guideimp4 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.2)
```



\



# Risk Behavior in April (riskapril)
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# riskapril
mean.riskapril <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(riskapril), funs(Wighted.mean.riskapril = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.riskapril <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(riskapril), funs(Wighted.sd.riskapril = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

riskapril <- cbind(mean.riskapril,sd.riskapril)
riskapril <- riskapril[,-3]
```

\

## Plot for Risk Behavior in April (Wighted mean)
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
riskapril %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean.riskapril,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean.riskapril,2))) +
  geom_bar(stat="identity", fill="deepskyblue3") + ylab('Risk Behavior (Wighted mean) in April') +
  theme_bw() + ggtitle("Risk Behavior (Wighted mean) for each neighborhood in April") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```
\

## Plot for Risk Behavior in April (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
riskapril %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd.riskapril,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd.riskapril,2))) +
  geom_bar(stat="identity", fill="cadetblue") + ylab('Risk Behavior (Wighted sd) in April') +
  theme_bw() + ggtitle("Risk Behavior (Wighted sd) for each neighborhood in April") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Risk Behavior in April
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))
```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

riskapril.map <- merge(nbhd_geo, riskapril, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(riskapril.map) + tm_polygons(c('Wighted.mean.riskapril','Wighted.sd.riskapril'), palette=list("Greens","Blues"), style = "cont", title = c("Mean Risk Behavior in April", "sd Risk Behavior in April")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\

## Faceted histograms by neighborhood (weighted) - Risk Behavior in April - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = riskapril, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Risk Behavior in April') +
  ggtitle("Faceted histograms by neighborhood")
```


\

## Faceted histograms by neighborhood (weighted) - Risk Behavior in April - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = riskapril, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Risk Behavior in April') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```


\



## Correlation between means and sds for Risk Behavior in April
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.riskapril <- round(cor(riskapril$Wighted.mean.riskapril, riskapril$Wighted.sd.riskapril),2)
print(sprintf("The correlation between means and sds for Risk Behavior in April is: %s", cor.riskapril))
```


\

## Anova for Risk Behavior in April without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.riskapril <- aov(riskapril ~ BNUName, data = final.nsf)
summary(anova.riskapril)
```

\

## Anova for Risk Behavior in April with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.riskapril <- lm(riskapril ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.riskapril)
```


\


# Risk Behavior in Summer (risklast7)
\


```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# risklast7
mean.risklast7 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(risklast7), funs(Wighted.mean.risklast7 = weighted.mean(., MERNRWGT, na.rm=TRUE)))

sd.risklast7 <- final.nsf %>%
  group_by(BNUName) %>% 
  summarise_at(vars(risklast7), funs(Wighted.sd.risklast7 = sqrt(Hmisc::wtd.var(., MERNRWGT, na.rm=TRUE))))

risklast7 <- cbind(mean.risklast7,sd.risklast7)
risklast7 <- risklast7[,-3]
```

\

## Plot for Risk Behavior in Summer (Wighted mean)


\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
risklast7 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.mean.risklast7,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.mean.risklast7,2))) +
  geom_bar(stat="identity", fill="darkorchid4") + ylab('Risk Behavior in Summer (Wighted mean)') +
  theme_bw() + ggtitle("Risk Behavior (Wighted mean) for each neighborhood in Summer") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


## Plot for Risk Behavior in Summer (Wighted sd)
\
```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
risklast7 %>%
  mutate(BNUName = fct_reorder(BNUName, desc(round(Wighted.sd.risklast7,2)))) %>%
  ggplot(aes(x=BNUName, y=round(Wighted.sd.risklast7,2))) +
  geom_bar(stat="identity", fill="firebrick4") + ylab('Risk Behavior in Summer (Wighted sd)') +
  theme_bw() + ggtitle("Risk Behavior (Wighted sd) for each neighborhood in Summer") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) 
```


\


## Maps for Risk Behavior in Summer
\

```{r,echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd_geo <- st_read(dsn="~/Desktop/Beacon_Nbhd/Beacon_Neighborhoods.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_geo$BNU_Name <- ifelse(nbhd_geo$BNU_Name == "Roxbury : Highland Park/ Sav-Mor/ Washington Park", "Roxbury", ifelse(nbhd_geo$BNU_Name == 'Dorchester Central:   Fields Corner; Bowdoin; Codman Square; Uphams Corner', "Dorch. Central", ifelse(nbhd_geo$BNU_Name == 'Jamaica Plain: Mission Hill', "J.P.: Mission Hill", ifelse(nbhd_geo$BNU_Name == "East Boston: Eagle Hill/ Harbor View", "East Boston: E.H.", ifelse(nbhd_geo$BNU_Name == "Central: North End", "Central N.E.", ifelse(nbhd_geo$BNU_Name == "North Dorchester:   Columbia Point", "Dorch. North", ifelse(nbhd_geo$BNU_Name == "East Boston: Central Maverick/ Jeffries Point", "East Boston", ifelse(nbhd_geo$BNU_Name == "Central: West End", "Central W.E.", ifelse(nbhd_geo$BNU_Name == "South Dorchester : Ashmont/Neponset", "Dorch. South", ifelse(nbhd_geo$BNU_Name == "Jamaica Plain: Jamaica/ Hyde Square/ Forest Hills", "J.P.", ifelse(nbhd_geo$BNU_Name == "Central: Chinatown/ Bay Village", "Central", ifelse(nbhd_geo$BNU_Name == 'Roxbury: Dudley/ Lower Roxbury', "Lower Roxbury", ifelse(nbhd_geo$BNU_Name == "Allston", "Allston", ifelse(nbhd_geo$BNU_Name == "Back Bay", "Back Bay", ifelse(nbhd_geo$BNU_Name == "Beacon Hill", "Beacon Hill", ifelse(nbhd_geo$BNU_Name == "Brighton", "Brighton", ifelse(nbhd_geo$BNU_Name == "Charlestown", "Charlestown", ifelse(nbhd_geo$BNU_Name == "Fenway/Kenmore", "Fenway/Kenmore", ifelse(nbhd_geo$BNU_Name == "Hyde Park", "Hyde Park", ifelse(nbhd_geo$BNU_Name == "Mattapan", "Mattapan", ifelse(nbhd_geo$BNU_Name == "Roslindale", "Roslindale", ifelse(nbhd_geo$BNU_Name == "Seaport", "Seaport", ifelse(nbhd_geo$BNU_Name == "South Boston", "South Boston", ifelse(nbhd_geo$BNU_Name == "South End", "South End", ifelse(nbhd_geo$BNU_Name == "West Roxbury", "West Roxbury", NA)))))))))))))))))))))))))
```

\

\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

risklast7.map <- merge(nbhd_geo, risklast7, by.x = "BNU_Name", by.y = 'BNUName' ,all.x=TRUE)

tmap_mode('view')
tm_shape(risklast7.map) + tm_polygons(c('Wighted.mean.risklast7','Wighted.sd.risklast7'), palette=list("Purples","Oranges"), style = "cont", title = c("Mean Risk Behavior in Summer", "sd Risk Behavior in Summer")) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_basemap(server = c('OpenStreetMap')) + tmap_options(show.messages = FALSE)
```


\

## Faceted histograms by neighborhood (weighted) - Risk Behavior in Summer - Count
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
ggplot(final.nsf, aes(x = risklast7, weights= MERNRWGT)) + geom_histogram(binwidth = 0.4) + theme_bw() +
  facet_wrap(~ BNUName) + xlab('Risk Behavior in Summer') +
  ggtitle("Faceted histograms by neighborhood")
```



\

## Faceted histograms by neighborhood (weighted) - Risk Behavior in Summer - Proportion
\


```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}

ggplot(final.nsf, aes(x = risklast7, weights= MERNRWGT)) + geom_histogram(aes(y=..count../sum(..count..)))+ theme_bw() +
  facet_wrap(~ BNUName) + xlab('Risk Behavior in Summer') + ylab("Proportion") + 
  ggtitle("Faceted histograms by neighborhood-Proportion-weighted")

```


\

## Correlation between means and sds for Risk Behavior in Summer
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cor.risklast7 <- round(cor(risklast7$Wighted.mean.risklast7, risklast7$Wighted.sd.risklast7),2)
print(sprintf("The correlation between means and sds for Risk Behavior in Summer is: %s", cor.risklast7))
```


\


## Anova for Risk Behavior in Summer without weights
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.risklast7 <- aov(risklast7 ~ BNUName, data = final.nsf)
summary(anova.risklast7)
```

\


## Anova for Risk Behavior in Summer with weights (Merged Nonresponse Weights)
\

```{r echo=FALSE, warning=FALSE, message=FALSE, comment=""}
anova.risklast7 <- lm(risklast7 ~ BNUName, data = final.nsf, weights = MERNRWGT)
anova(anova.risklast7)
```

\

